Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in the Raspberry Pi

### 2016-06-28 conclusions.tex
New abstract and new conclusions

\label{sec:conclusions}
Given the need for low-cost, easy to configure, testbeds that enable
reproducible results, we provide a in-depth description of Aalborg
University's \ac{Raspi} testbed and how to guarantee replicable
results and managing scaling of the system.  We also provide a
performance evaluation for network coding schemes, focusing on
processing speed and energy behaviour for two \ac{Raspi} models,
including algorithms that exploit \ac{SIMD} instructions and multicore
capabilities of the \ac{Raspi} 2. Our measurements show that
processing speeds of more than 80 Mbps and 800 Mbps are attainable for
the \ac{Raspi} model 1 and 2, respectively, for a wide range of
network coding configurations and maintaining a processing energy
below 1 nJ/bit (or even an order of magnitude lower) in similar
configurations. Future work in the use of \ac{Raspi} devices will
focus on expanding the setup and automation of tasks to run the
testbed, configure specified network topologies (e.g., with specific
connectivity or packet loss ratios), reserve the use of these
sub-networks for running tailored experiments, and opening the use of
the testbed beyond our team at Aalborg University.

>>>>

\label{sec:conclusions}
Given the usefulness of the \ac{Raspi} as a low-complex
processing node in large-scale networks and network coding
techniques against state-of-the-art routing, we provide
a performance evaluation of network coding schemes focusing on
processing speed and energy consumption for two \ac{Raspi} models.
The evaluation includes algorithms that exploit both \ac{SIMD}
instructions and multicore capabilities of the \ac{Raspi} 2. Our
measurements show that processing speeds of more than 80 Mbps and 800
Mbps are attainable for the \ac{Raspi} model 1 and 2, respectively,
for a wide range of network coding configurations and maintaining
a processing energy below 1 nJ/bit (or even an order of magnitude lower)
in similar configurations. For the use of multithreading, we quantify
processing gains ranging from 2$\times$ for $g = 16$ to 13$\times$ for
$g = 1024$ when employing 4 threads each in a different core. Future
work in the use of \ac{Raspi} devices will focus on considering: (i)
the performance of the \ac{Raspi} in scenarios with synthetic packet
losses, (ii) wireless networks where real packet losses can occur
and (iii) other topologies such as broadcast or
cooperative scenario to compare with theoretical results in order to
evaluate the performance of different network codeswith the \ac{Raspi}.
